Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-08 paper.tex
Add value over time figure.

% Document-specific packages
\usepackage{epigraph}
\usepackage[flushleft]{threeparttable}

@@

@@

>>>>

% Document-specific packages
\usepackage{epigraph}
\usepackage[flushleft]{threeparttable}
\usepackage{graphicx}

@@

\bigskip

@@

\begin{figure}
\includegraphics[width=3.33in,height=1.67in]{fig-val-iter.pdf}
\caption{
Mean agent solution value over time, averaged over 100 trials.
The left and right figures show results for agent networks with the probability of
rewiring set to 0 and 1, respectively.
In both, local strategies are less efficient and more performant than nonlocal.
The consensus strategy is both more efficient and more performant than others,
with its performance increasing with higher rewiring.
\label{fig:val-iter}
}
\end{figure}
